VIPE: Virtualized Intermittently-Powered Executor

### 2017-07-19 paper/background.tex
added section on the type of computing HW

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/code_demo_incosistency}
	%	for (byte = 0; byte < nBytes; ++byte){\\
	%	checkpoint();\\
		%data = reflectData(message\[byte\]) $^$ (remainder >> (WIDTH - 8));\\
		%remainder = crcTable[data] $^$ (remainder << 8);}
	\caption{Code demonstrating WAR and volatile memory checkpointing.}
	\label{fig:code_demo_incosistency}
\end{figure}

@@

>>>>

\begin{figure}
	\centering
	\fbox{\texttt{text}}
	%\includegraphics[width=0.25\columnwidth]{figures/code_demo_incosistency}
	%	for (byte = 0; byte < nBytes; ++byte){\\
	%	checkpoint();\\
		%data = reflectData(message\[byte\]) $^$ (remainder >> (WIDTH - 8));\\
		%remainder = crcTable[data] $^$ (remainder << 8);}
	\caption{Code demonstrating WAR and volatile memory checkpointing.}
	\label{fig:code_demo_incosistency}
\end{figure}

@@

\subsection{Assumption on the Type of Computing Hardware}
\label{sec:background_hardware}

We assume that we operate on the microcontroller (more generally, computing hardware) equipped with a mix of volatile and non-volatile memory~\cite{}, such as FLASH, Ferroelectric RAM or Magnetoresistive RAM. \sys does not assume to rely on specific memory type (either volatile or non-volatile), in contrary to earlier works targeting non-volatile processors~\cite{ratchet}. Actually, \sys will exploit the properties of both memory types to maximize performance metrics of the program being executed. We make \sys able to I/O operations, however we do not enable the scheduling of operations (which nota bene forms a foundation for a simple runtime). All in all, our hardware model follows in assumptions the two most relevant intermittently-powered execution environments~\cite{alpaca,chain}.
